---
title: 'Homophily in Voting Behaviour: Evidence from Preferential Voting'
author: "Štěpán Mikula"
date: "4 2 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE}
library(dtplyr)
library(tidyverse)
library(fixest)
library(modelsummary)

rm(list = ls())

# Read data
res_obce <- read_tsv("rdata_RP.zip") %>% 
  mutate(
    across(
      .cols = c(maxPORCISLO,OBEC,year),
      as.character
    )
  ) %>% 
  mutate(
    across(
      .cols = c(pref,POC_HLASU),
      as.integer
    )
  ) 
```
Variables:
- `pref`...number of preferential votes for the candidate
- `homo_municipality`...candidate is resident of the municipality
- `homo_age`...share of population of the same age
- `homo_educ`...share of population with the same education (tertiary/other)
- `homo_gender`...share of population of the same gender
- `homo_isco`...share of population of the same occupation (ISCO1)
- `year`...year of elections (elections ID)
- `ballot`...ballot (electoral list) ID
- `POC_HLASU`...number of votes casted for the party
- `total_fe`...candidate ID (elections specific)
- `OBEC`...municipality ID (CISOB)
- `maxPORCISLO`...number of candidates on the ballot
- `small`...municipality with population below median


```{r}
modell <- list(
  formula(pref ~ homo_educ | total_fe + OBEC  + maxPORCISLO),
  formula(pref ~ homo_isco | total_fe + OBEC  + maxPORCISLO),
  formula(pref ~ homo_age | total_fe + OBEC  + maxPORCISLO),
  formula(pref ~ homo_gender | total_fe + OBEC  + maxPORCISLO),
  formula(pref ~ homo_municipality | total_fe + OBEC + maxPORCISLO),
  formula(pref ~ homo_educ + homo_isco + homo_age + homo_gender + homo_municipality | total_fe + OBEC + maxPORCISLO)
) 
```

#### Table 3

```{r}
baseline <- modell %>% 
  map(
    feglm,
    data = res_obce,
    offset = ~log(POC_HLASU),
    cluster = c("ballot"),
    family = quasipoisson
  )

etable(baseline)
```

#### Table 4

```{r}
baseline_small <- modell %>% 
  map(
    feglm,
    data = filter(res_obce,small),
    offset = ~log(POC_HLASU),
    cluster = c("ballot"),
    family = quasipoisson
  )

etable(baseline_small)
```

#### Table A.1

```{r}
dta <- filter(res_obce, small, !homo_municipality)

baseline_small_munic <- modell[-5] %>% 
  map(
    feglm,
    data = dta,
    offset = ~log(POC_HLASU),
    cluster = c("ballot"),
    family = quasipoisson
  )

etable(baseline_small_munic)
```

#### Table A.2

```{r}
rs_small <- filter(res_obce, small)

baseline_small_year_w <- modell %>% 
  map(
    feglm,
    data = rs_small,
    offset = ~log(POC_HLASU),
    cluster = c("ballot"),
    family = quasipoisson,
    weights = rs_small$POC_HLASU
  )

etable(baseline_small_year_w)
```